### 2016-11-17 paper/evaluation.tex
fixes

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\vspace{-3ex}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
    \Fix{On the left side, results from sequential execution; the right side,
    results from default execution.}}
\end{figure}

Considering the groups \emph{medium} and \emph{long}, we investigated
the relation between number of tests cases and time cost from
subjects.  \Fix{elaborate: As expected, Figure~\ref{fig:scatters}
reveals that the number of tests cases are not related to the elapsed
time.  \Fix{explain briefly what dominates a test execution/types of
tests}.  We ignored outliers for better visualization.} Results
indicate that \Fix{...conclusion...}.

>>>>

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    morekeywords={o, DskipTests, Dmaven, javadoc, skip},
    deletekeywords={true}
}
\begin{lstlisting}
mvn clean install -DskipTests -Dmaven.javadoc.skip=true
mvn -o test -Dmaven.javadoc.skip=true
\end{lstlisting}
\caption{\label{fig:mvn-execution} Compiling and testing a Maven
    subject: line 1 compiles all subject's source artifacts and make
    them available in a local repository (\ie, directory \emph{.m2} in
    the user's home directory); line 2 runs the tests in offline mode
    ignoring javadoc generation.}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{results/rq1/plots/piechart.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed
    time on test execution ($t$): short execution ($t < 1m$), medium 
    execution ($1m \leq t < 5m$), and long execution ($5m \leq t$).
    \Fix{On the left side, results from sequential execution; on the
    right side, results from default execution.}}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X}
subjects), we investigated the relationship between the number of
tests cases and the time cost from subjects.  Figure~\ref{fig:scatter}
shows two scatter plots with We created a scatter plot for each group
and computed the correlation of time cost and number of tests.
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that
the number of tests cases are not related to the elapsed time.
\Fix{explain briefly what dominates a test execution/types of tests}.
We ignored outliers for better visualization.} Results indicate that
\Fix{...conclusion...}.
